\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{deliriumcoder}

\usepackage[scale=0.75]{geometry}
\nopagenumbers{}

\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{lastpage}

\firstname{Oscar}
\familyname{Campos}
\title{Software Engineer}
\address{4 The Hedgerows Brighton Road}{Foxrock Village, Dublin, Ireland}
\mobile{+353 83 150 6861}
\email{oscar.campos@member.fsf.org}
\homepage{http://blog.deliriumcoder.com}

\cfoot{\footnotesize{This document has been built with \LaTeX}}

\begin{document}
\maketitle

\section{Profile}
I am IT Consultant and Software Developer with more than
twelve years of experience in the IT industry. I am very interested in
backend-frontend based applications specially web applications and scalable
systems specially builded with {\bfseries Python}.

I am also the founder of \httplink[Goliat]{http://goliat.open-phoenix.com}
the Open Phoenix IT Web Applications Framework and \httplink[Mamba]{https://github.com/DamnWidget/mamba} a new and better framework that uses Twisted and Storm internally. I am self taught, Internet has been my great library, I think it's of
vital importance to give back to the society what we take from it, and that's
why I am blogger and I write articles in \httplink[Genbeta Dev]{http://www.genbetadev.com}.

\section{Employment History}
% Dedsert LTS - Dublin

\cventry{2014--Present}{Backend Development Team Leader}{Dedsert Ltd}{Dublin}{}{
Dedsert is an startup company in the business of online gaming that went live in 2012.\newline{}
{\bfseries Key Projects}:
\begin{itemize}
\item {\bfseries BetBright} (\httplink[https://www.betbright.com/sports]{https://www.betbright.com/sports}):
  \begin{itemize}
  \item Betbright are all about taking the really good things from online gambling, making them better and getting rid of all of the things that people find annoying. We've set out to provide you with an experience that we, as sports enthusiasts and people who like to bet, is simply better than the rest.\newline{}
  \newline{}Betbright understand what people really want and what's important to them. We also understand what people don't like and what's not important. We want to avoid betting jargon, complicated forms and irrelevant content. We'd rather never hear from an online gambling service than receive random communication and emails pushing us bets and info that we have no interest in.
  \end{itemize}
\end{itemize}
{\bfseries \textit{As Backend Development Team Leader I am responsible for}}\newline{}
Coordinate the development team, conduit the Scrum methodology, design and review the architecture of the software and improve the system with optmizations, fixes and proposals.\newline{}
{\bfseries \textit{Key Technology Used}}\newline{}
Jira, Python, Twisted, Mamba, MySQL, Apache, Nginx, GNU/Linux, Bottle, AngularJS
{\bfseries \textit{Alter Roles}}\newline{}
Scrum Master
}

% Dedsert LTS - Dublin

\cventry{2012--December 2013}{Senior Python Developer}{Dedsert Ltd}{Dublin}{}{
Dedsert is an startup company in the business of online gaming that went live in 2012.\newline{}
{\bfseries Key Projects}:
\begin{itemize}
\item {\bfseries BetBright} (\httplink[https://www.betbright.com/sports]{https://www.betbright.com/sports}):
  \begin{itemize}
  \item Betbright are all about taking the really good things from online gambling, making them better and getting rid of all of the things that people find annoying. We've set out to provide you with an experience that we, as sports enthusiasts and people who like to bet, is simply better than the rest.\newline{}
  \newline{}Betbright understand what people really want and what's important to them. We also understand what people don't like and what's not important. We want to avoid betting jargon, complicated forms and irrelevant content. We'd rather never hear from an online gambling service than receive random communication and emails pushing us bets and info that we have no interest in.
  \end{itemize}
\end{itemize}
{\bfseries \textit{As Senior Python Server Developer I am responsible for}}\newline{}
Develop new features for the application, review the code of junior programmers and serve as mentor for them as well. Decide the design of the new features of the application and support other departments in the development of new products and ideas. I am responsible for optimize and refactor legacy code that the application uses and support other programmers with code styling and good programming practices. Recently we introduced a technology that I developed and it's available under the GPL license on \httplink[https://github.com/DamnWidget/mamba]{https://github.com/DamnWidget/mamba}.\newline{}
{\bfseries \textit{Key Technology Used}}\newline{}
Python, Twisted, Mamba, MySQL, Apache, GNU/Linux, Bottle, ZeroMQ
}

% Webalianza IT - Gipuzkoa
\cventry{2011--2012}{Senior Software Developer}{Webalianza IT S.L.}{San Sebastian}{}{Webalianza is an IT Consulting company with more than thirteen years of experience in the IT market of Basque Country with important clients in the research and science like CIC nanoGUNE (\httplink[]{http://www.nanogune.eu/en}). Webalianza main products are based on ExtJS, PHP, Scala, VMWare, Unix, Linux, NetAPP and Cisco technologies.\newline{}
{\bfseries Key Projects}:
\begin{itemize}
\item {\bfseries Gaia New Exchange} (\httplink[http://www.gainetexchange.com/drupal/]{http://www.gainetexchange.com/drupal/}):
  \begin{itemize}
  \item GNE it's a service to provide an Universal business channel operations to companies and organizations making possible to share invoices, bank operations and another type of documents between different information services like ERP's or CRM's using Scala for the backend mechanism.
  \end{itemize}
\item {\bfseries NanoPEOPLE}
  \begin{itemize}
  \item NanoPEOPLE is a full employees, timesheets, holidays, calendars, meetings, lab  equipment and other science research solution crafted in PHP and ExtJS 3.x for the San  Sebastian Cooperative Investigation Center nanoGUNE.
  \end{itemize}
\item {\bfseries NanoSECURITY}
  \begin{itemize}
  \item Python system application running in an Ubuntu GNU/Linux virtual machine that counts people inside the research building in nanoGUNE to arm it automatically when people counter reach zero or disarm it when any person gets inside again.
  \end{itemize}
\item {\bfseries Oversys CRM}
  \begin{itemize}
  \item Oversys CRM is a PHP/ExtJS CRM web application for the international group of companies specialized in technology for the whole process of the manufacturing of corrugated cardboard packaging products \httplink[Oversys]{http://www.oversys.es}.
  \end{itemize}
\end{itemize}
{\bfseries \textit{As Senior Software Developer I am resposible for}}\newline{}
I am responsible for developing all those projects as part of a small team of two developers and one system administrator. I am also responsible for the correct implementation of the SCRUM methodology for the GNE project. I used Python, Scala, PHP, JavaScript, CSS and HTML in those projects.\newline{}
{\bfseries \textit{Key Technology Used}}\newline{}
Scala, PHP, Python, C\#.NET, Play 2 Framework, jQuery, ExtJS, VMware, GNU/Linux, MySQL, RESTfull websevices, SBT, SCRUM.
}

%Open Phoenix IT - Jaén
\cventry{2009--2012}{IT Consultant and Chief Business Officer (Fellow)}{Open Phoenix IT S.C.A.}{Ja\'en}{}{Open Phoenix IT is a Cooperative Company of Associated Work that extensively works with Free Software and Open Source solutions. They also develops and distributes Free Software as \httplink[Goliat]{http://goliat.open-phoenix.com}, \httplink[Backharddi-NG]{http://backharddi-ng.open-phoenix.com} or \httplink[ITE eXe Learning]{https://forja.cenatic.es/projects/iteexe/}.\newline{}
{\bfseries Key Projects}:
\begin{itemize}
\item {\bfseries GCES}
  \begin{itemize}
  \item GCES is an acronym for School Canteens Management (Gestión de Comedores Escolares in spanish), full featured OpenERP module crafted for the spanish catering company Royal Menu Catering S.L. GCES allow the planning of hundred of School Canteens.
  \end{itemize}
\item {\bfseries ITE MGM}
  \begin{itemize}
  \item ITE MGM is a detached full featured module for Moodle 1.9 LMS. The module was developed for the Institute of Educative Technologies (now National Institute of Educative and Learning Technologies for the Teachers) of the spanish education ministry. MGM is a big an independent module for the massive learning platform Moodle written in PHP using Test Driven Development as design methodology.\newline{}
  \newline{}MGM is already deployed and it's running in the main Moodle server in the ministry and serve as enrollment mechanism for the enrollment and management of all the spanish state public schools teachers.\newline{}
  \newline{}Code can be found \httplink[here]{http://forja.cenatic.es/projects/itemgm} and \httplink[here]{https://github.com/DamnWidget/ITEMoodleOP}
  \end{itemize}
\end{itemize}
{\bfseries \textit{As IT Consultant I was responsible for}}\newline{}
On GCES I was responsible for develop a mashup service between a Twisted Web Server developed with Goliat and the OpenERP server through a XMLRPC interface using ExtJS 3 as frontend for the Goliat service. Design a full featured calendar for the GUI creating new ExtJS widgets from zero. A video of those interfaces can be checked at:\newline{}
\newline{}  - \httplink[Video One]{http://www.youtube.com/watch?feature=player_embedded&v=bkaJqalWuSg}\newline{}
  - \httplink[Video Two]{http://www.youtube.com/watch?feature=player_embedded&v=0jRS_LbOdZM}\newline{}
\newline{}I was also responsible for the full development of Moodle ITE MGM module writing its code in PHP and keeping the entire module independent from the Moodle core to make possible future full system upgrades.
I worked on GNU/Linux system development and was responsible for the correct implementation of the SCRUM methodology at projects and Open Phoenix goliat framework and main site web pages development.\newline{}
{\bfseries \textit{As Chief Business Officer I was responsible for}}\newline{}
Open Phoenix IT is a small company so I had multi-role on it. As CBO I was responsible for marketing, discover new business strategies and go to the IT sector events to give lectures about Free Software, programming, social economy and technology for new business models.\newline{}
{\bfseries \textit{Key Technology Used}}\newline{}
Python, PHP, C/C++, JavaScript, OpenERP 5, ExtJS 3, Twisted 10.2.0, Goliat 0.1, Symfony 1.2, jQuery, Qt 4.4, XMLRPC, SQL, Apache, GNU/Linux, FreeBSD, Moodle 1.9/2.0, Liferay, J2SE 6, Kinout, LibreOffice, LaTeX
}

% EDM-IDE Seneca Mancha Real, Jaén
\cventry{2007--2009}{IT Consultant specialized in GNU/Linux and Free Software}{EDM-IDE Seneca}{Mancha Real, Ja\'en}{}{EDM was the biggest hardware assembler in Spain, IDE Seneca was a Consultant Services company that offered IT services to EDM.\newline{}
{\bfseries Key Projects}:
\begin{itemize}
\item {\bfseries Backharddi}:
  \begin{itemize}
  \item It was an efficient physical storage drives cloning tool that works with partitions formated in: FAT16/32, HPFS, JFS, XFS, UFS, HFS, ReiserFS v3, Ext2/3 and NTFS. The project is now unmaintained and the only information available is on \httplink[web.archive.org]{http://web.archive.org/web/20080928135627/http://www.edmanufacturer.es/news/2008/04_09_backharddi.asp}
  \end{itemize}
\item {\bfseries MAX GNU/Linux distribution}
  \begin{itemize}
  \item \httplink[MAX]{http://www.educa2.madrid.org/web/max/} is the Community of Madrid GNU/Linux distribution. It's based on Ubuntu GNU/Linux and is developed by some private companies that supports the Free Software and volunteer developers around Spain.
  \end{itemize}
\item {\bfseries GNU/Linux driver and backport development}
  \begin{itemize}
  \item I backported some drivers from higher Linux distributions or kernel versions to lower ones in order to allow old systems to work with new hardware (from China basically). I wrote some kernel module modifications for EDM too.
  \end{itemize}
\item {\bfseries EDM Internet PC-TV project}
  \begin{itemize}
  \item In 2008 I worked in an unfinished project to build a TV with an small Intel Atom \textregistered based PC assembled inside a common back cover much before Google release their Google TV but the company went bankrupt with the very early crisis damages before we could finish the project. The operating system selected was Gentoo GNU/Linux with MythTV running on it.
  \end{itemize}
\end{itemize}
{\bfseries \textit{As an IT Consultant specialized in GNU/Linux and Free Software I was responsible for}}\newline{}
Backport and develop GNU/Linux drivers usually for Operating Systems based on old versions of Ubuntu and Debian. Develop a C++ frontend for Backharddi cloning media system using the Qt Toolkit. Develop lot of small DevOps applications in Python to manage GNU/Linux systems. Create Operating Systems master discs to massively clone it. Optimize Gentoo GNU/Linux boot process time and size for PC-TV project. Develop several .deb packages for MAX distribution. Write several documentation pages for MAX distribution. System Administration under GNU/Linux and write Python internal applications for massively OS OEM clone and other management tasks.\newline{}
{\bfseries \textit{Key Technology Used}}\newline{}
Several GNU/Linux distributions, C/C++, Python, JavaScript, PHP, KDEvelop, QtCreator, Qt Tookit, PyQt, PyGTK, Twisted, MythTV, Backharddi.
}

% Freelance, Jaén
\cventry{2005--2007}{Freelance}{}{Spain}{}{I worked as freelance for different companies doing several tasks.\newline{}
{\bfseries Key Projects}:
\begin{itemize}
\item {\bfseries Lineage 2 World}:
  \begin{itemize}
  \item Lineage 2 World was a private Lineage2 Off server where I worked as C++ developer doing DLL injection and reverse engineering for almost two years. I was GM in their server as well.
  \end{itemize}
\item {\bfseries Mercenary Web Developer}
  \begin{itemize}
  \item Web development for several customers
  \end{itemize}
\end{itemize}
{\bfseries \textit{As Freelance I was responsible for}}\newline{}
Develop web sites and applications for customers.\newline{}
Implement new features to binary applications in Win64 architecture through DLL injection and reverse engineering techniques.\newline{}
{\bfseries \textit{Key Technology Used}}\newline{}
C++, IDA Pro Disassembler, OllyDbg, Hexedit, Visual Studio 2005, Ultraedit, L2Off Toolsets, HTML, PHP, JavaScript, CSS, Apache, MySQL.
}

% Omicron Systems, Jaén
\cventry{2003--2004}{Project Manager (Fellow)}{Omicron Systems, CamposOlivera S.L.L}{Ja\'en}{}{Omicron-Systems Campos Olivera S.L.L, was a small company founded by me and other fellows.\newline{}
{\bfseries Key Projects}:
\begin{itemize}
\item {\bfseries Inytel CRM System}:
  \begin{itemize}
  \item CRM web application built in PHP 4, HTML and JavaScript for the Spanish Vodafone mobile supplier Inytel for tracking IMEI numbers, marketing and customers management.
  \end{itemize}
\end{itemize}
{\bfseries \textit{As Project Manager I was responsible for}}\newline{}
Design the application, and system architecture for the suite. Manage the project and help with software development when needed.\newline{}
{\bfseries \textit{Key Technology Used}}\newline{}
PHP4, HTML, CSS, JavaScript, SuSE Linux 8.1, Apache 1.23, MySQL 4.x
}

% education
\section{Education}
\cventry{1999--2002}{Diploma}{I.P.F.P El Cabanyal}{Valencia}{\textit{Superior Grade on Software Development}}{}
\section{Additional Education}
\cvitem{1999--2002}{
\begin{itemize}
\item Internet initiation, 200 hours, summer 1998
\item C++ development, 300 hours, summer 1999
\end{itemize}
}

% certificaciones
\section{Certifications}
\cvitem{May 2012}{CSM (Certified Scrum Master) number 000191155}
\cvitem{2012}{Certificate number 28923016010491200090 from the Spanish Culture, Sports and Education Ministery for participate as tutor at the 2012 Moodle for Beginners course at Instituto Nacional de Tecnologías Educativas y de Formación del Profesorado.}
\cvitem{Dec 2012}{MongoDB for Developers} https://education.10gen.com/downloads/certificates/235e8a5a7f124ca5adefa5dff8401c16/Certificate.pdf


% Languages
\newpage
\section{Languages}
\cvitemwithcomment{Spanish}{Native}{}
\cvitemwithcomment{Catal\'an}{Intermediate}{}
\cvitemwithcomment{English}{Intemediate}{}

% Skills
\renewcommand{\listitemsymbol}{-~}
\section{Skills}
\subsection{Programming Languages}
\cvlistitem{Python, PHP, Scala, JavaScript, C/C++}
\subsection{Web Related}
\cvlistitem{CSS3, HTML5}
\subsection{Ajax}
\cvlistitem{ExtJS, jQuery, Pure JavaScript}
\subsection{Frameworks}
\cvlistitem{Django, Symfony 1.2, Twisted, Play2 (Scala)}
\subsection{IDE}
\cvlistitem{Eclipse, QtCreator}
\subsection{Text Editors}
\cvlistitem{vi, Sublime Text 2}
\subsection{Databases}
\cvlistitem{MySQL, PostgreSQL, MongoDB}
\subsection{Source Control}
\cvlistitem{Git, Subversion}
\subsection{Operating Systems}
\cvlistitem{GNU/Linux, Mac OS X, Other UNIX, Windows}
\subsection{Servers}
\cvlistitem{Apache, Nginx}

\section{Technical Reviews that I made}
% PySide
\cvitem{{\bfseries PySide GUI Application Development}}{
{\bfseries Publisher}\newline{}
Packtpub\newline{}
{\bfseries ISBN 13}\newline{}
9781849699594\newline{}
{\bfseries Description}\newline{}
Elegantly built GUI applications are always a massive hit among users. PySide is an open source software project that provides Python bindings for the Qt cross-platform UI framework. Combining the power of Qt and Python, PySide provides easy access to the Qt framework for Python developers and also acts as an excellent rapid application development platform available on all major operating systems.\newline{}This book aims to help you develop GUI applications easily using PySide. Python is easy to learn and use and its programs are relatively shorter than those written in other programming languages like C++ or Java. This book will introduce you to user interface programming in Python, allowing you to develop real-time applications in a shorter amount of time.\newline{}This book will take you through everything you need to know to develop UI applications. You will learn about installing/building PySide in various major operating systems as well as the basics of GUI programming. The book will then move on to discuss event management, signals and slots, and the widgets and dialogs available with PySide. Database interaction and manipulation is also covered.\newline{}In a nutshell, this book is great for learning how to program applications with GUI and for mastering how to develop your own applications and how to run them across platforms.\newline{}
{\bfseries Book URL}\newline{}
\httplink[http://www.packtpub.com/pyside-gui-application-development/book]{http://www.packtpub.com/pyside-gui-application-development/book}
}

\section{Open Source projects where I contribute in some way}
% Python
\cvitem{{\bfseries Python}}{
{\bfseries Description}\newline{}
Python is a programming language that lets you work more quickly and integrate your systems more effectively. You can learn to use Python and see almost immediate gains in productivity and lower maintenance costs.\newline{}
{\bfseries Contribution}\newline{}
I contribute with the Python Software Foundation and the Python project maintaining the \httplink[Pydotorg Website]{http://www.python.org} and providing Tutorship to new Python users in several Python mailing lists.\newline{}
{\bfseries Project URL}\newline{}
\httplink[http://www.python.org]{http://www.python.org}
}

% Anaconda
\cvitem{{\bfseries anaconda}}{
{\bfseries Description}\newline{}
Anaconda is one of the most widely used Python development extensions for Sublime Text 3. Anaconda is a full python development suite including autocompletion, code linting, IDE features, autopep8 formating, McCabe complexity checker and Vagrant for Sublime Text 3 using Jedi, PyFlakes, pep8, PyLint, pep257 and McCabe.\newline{}
{\bfseries Contribution}\newline{}
I completely wrote it.\newline{}
{\bfseries Project URL}\newline{}
\httplink[https://github.com/DamnWidget/anaconda]{https://github.com/DamnWidget/anaconda}
\httplink[https://sublime.wbond.net/packages/Anaconda]{https://sublime.wbond.net/packages/Anaconda}
}

% Mamba
\cvitem{{\bfseries mamba}}{
{\bfseries Description}\newline{}
Mamba is a high-level RAD Web Applicatios framework based on Twisted with steroids. Mamba is actually under heavy development and there is not a public alpha release yet but it should come in the next weeks.\newline{}
{\bfseries Contribution}\newline{}
I completely wrote it.\newline{}
{\bfseries Project URL}\newline{}
\httplink[https://github.com/DamnWidget/mamba]{https://github.com/DamnWidget/mamba}
}

% BuildBot
\cvitem{{\bfseries buildbot}}{
{\bfseries Description}\newline{}
BuildBot is an open-source framework for automating software build, test, and release processes. Buildbot can automate all aspects of the software development cycle (continuous integration, continuous deployment, release management) and any other process you can imagine.\newline{}
{\bfseries Contribution}\newline{}
I contributed with Buildbot adding a \httplink[Bitbicket changes hook, refactor and code sanitize for GitHub hook]{https://github.com/buildbot/buildbot/pull/715} and \httplink[added build status png view with SVG models for builds status]{https://github.com/buildbot/buildbot/pull/712}\newline{}
{\bfseries Project URL}\newline{}
\httplink[http://buildbot.net/]{http://buildbot.net/}
}

% Libsaas
\cvitem{{\bfseries libsaas}}{
{\bfseries Description}\newline{}
This is libsaas, a library to take the pain out of using SaaS APIs.\newline{}
It provides an abstraction layer on top of various APIs, taking care of constructing the URLs, serializing parameters and authentication. You just call Python methods and receive Python objects.\newline{}
{\bfseries Contribution}\newline{}
I added support for {\color{color3}BitBucket} and {\color{color3}MailRelay}.\newline{}
{\bfseries Project URL}\newline{}
\httplink[http://libsaas.net]{http://libsaas.net}
{\bfseries Source Repository}\newline{}
\httplink[https://github.com/ducksboard/libsaas]{https://github.com/ducksboard/libsaas}
}

% SublimeRope
\cvitem{{\bfseries SublimeRope}}{
{\bfseries Description}\newline{}
Adds Python completions and some IDE-like functions to Sublime Text 2, through the use of the \httplink[Rope]{http://rope.sourceforge.net/} library.\newline{}
{\bfseries Contribution}\newline{}
I added some Python Refactor features, fix some PEP-8 mistakes, moved some code to non-block Threading environment added new features and fixed some bugs. I am already a regular commiter for this project.\newline{}
{\bfseries Project URL}\newline{}
\httplink[https://github.com/JulianEberius/SublimeRope]{https://github.com/JulianEberius/SublimeRope}
}

% SublimePySide
\cvitem{{\bfseries SublimePySide}}{
{\bfseries Description}\newline{}
Sublime PySide adds Qt support for Sublime Text 2 on Python.\newline{}
{\bfseries Contribution}\newline{}
I completely wrote it.\newline{}
{\bfseries Project URL}\newline{}
\httplink[https://github.com/DamnWidget/SublimePySide]{https://github.com/DamnWidget/SublimePySide}
}

% Glosarium
\cvitem{{\bfseries Glosarium}}{
{\bfseries Description}\newline{}
Glosarium is a cross-platform application used by the Spanish Translation Team of the GNU project.\newline{}
{\bfseries Contribution}\newline{}
I completely wrote it.\newline{}
{\bfseries Project URL}\newline{}
\httplink[https://github.com/DamnWidget/glosarium]{https://github.com/DamnWidget/glosarium}
}

% IteMGM
\cvitem{{\bfseries IteMGM}}{
{\bfseries Description}\newline{}
IteMGM is an integral Moodle complex module integrating many independent parts to manage the Spanish Culture, Education and Sports ministry enrollment proccess.\newline{}
{\bfseries Contribution}\newline{}
I wrote it almost completely.\newline{}
{\bfseries Project URL}\newline{}
\httplink[http://forja.cenatic.es/projects/itemgm/]{http://forja.cenatic.es/projects/itemgm/}
}

% Goliat
\cvitem{{\bfseries Goliat}}{
{\bfseries Description}\newline{}
Goliat is a {\bfseries Web Applications Framework} written in \httplink[Python]{http://www.python.org/} and \httplink[JavaScript]{http://en.wikipedia.org/wiki/JavaScript} licensed under the \httplink[General Public License]{http://www.gnu.org/copyleft/gpl.html}. Goliat uses \httplink[Twisted]{http://twistedmatrix.com/trac/wiki}, \httplink[ExtJS]{http://www.extjs.com/}, \httplink[Orbited]{http://orbited.org/}, \httplink[Evoque]{http://evoque.gizmojo.org/} and \httplink[Storm]{https://storm.canonical.com/} to build web applications.\newline{}
{\bfseries Contribution}\newline{}
I completely wrote it.\newline{}
{\bfseries Project URL}\newline{}
\httplink[http://goliat.open-phoenix.com/]{http://goliat.open-phoenix.com/}
}

\newpage
% Interests
\section{Interests}
I like video games mainly RPG ones, comic books are another big passion. I also enjoy -if time allows it- of a good mountain bike route. I love good cinema and good serials if possible with a good dinner.

\section{References}
Very good – Available in my linkedin profile or by request.
\end{document}
